Title

### 2020-12-07 documents/DraftReport.Rmd
small edits

cols <- c("violetred4", "dodgerblue3", 'deepskyblue1', "#4aaaa5", "#a3d39c", "#f6b61c", "chocolate2", "red3")

@@

#functions to use for calling figures/tables
figs <- captioner(prefix = "Figure")
tbls <- captioner(prefix = "Table")

@@

sc <- c(1:5, 11:15)
nsim <- 25
pars <- c('fec', 'lambdaf', 'mean.p', 'mean.phi[1]', 'mean.phi[2]', 'p.surv', 'phi.nest')

@@

#scenarios without p.surv
sc <- c(6:10)
pars <- c('fec', 'lambdaf', 'mean.p', 'mean.phi[1]', 'mean.phi[2]', 'phi.nest')

>>>>

@@

#functions to use for calling figures/tables
figs <- captioner(prefix = "Figure")
tbls <- captioner(prefix = "Table")
cols <- c("violetred4", "dodgerblue3", 'deepskyblue1', "#4aaaa5", "#a3d39c", "#f6b61c", "chocolate2", "red3")

@@

# sc <- c(1:5, 11:15)
sc <- c(1:5)
nsim <- 5
pars <- c('fec', 'lambdaf', 'mean.p', 'mean.phi[1]', 'mean.phi[2]', 'p.surv', 'phi.nest')

@@

#scenarios without p.surv
# sc <- c(6:10)
sc <- c(6:9)

pars <- c('fec', 'lambdaf', 'mean.p', 'mean.phi[1]', 'mean.phi[2]', 'phi.nest')
